(tentative) Rotational Spectral Unmixing of Exoplanets

### 2016-11-21 paper/main.tex
adding missed figures
edits in a code to compute mock lightcurves

@@

%%%
\begin{eqnarray}
- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; f) \\
\mathcal{F}(\lambda, \Delta_t; f)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
\end{eqnarray}
%%%

...I think $\fast $ here should be zero mean for each $k$. 
%%%
\begin{equation}
\fast_{ik} \rightarrow ( \fast_{ik} - \fast^{(ave)}_k )
\end{equation}
%%%
In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast } (\Delta_t; f) = \lambda ^2 \mathcal{F}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
    \end{center}
    \end{minipage}
    \caption{Solution with smallest regularization term. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsubsection{Fitting with $\fast$}

@@

%%%
\begin{eqnarray}
- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; \fast) \\
\mathcal{\tilde F}(\lambda, \Delta_t; \fast)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
\end{eqnarray}
%%%

...I think $\fast $ here should be zero mean for each $k$. 
%%%
\begin{equation}
\fast_{ik} \rightarrow ( \fast_{ik} - \fast^{(ave)}_k )
\end{equation}
%%%
In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast } (\Delta_t; \fast) = \lambda ^2 \mathcal{\tilde F}$.

\subsubsection{Concerns}

%%%
\begin{itemize}
\item $\fast_{lk}$'s or $f_{lk}$'s are not mutually independent. (Sum is unity.) 
\item Same regularization 
\end{itemize}
%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$.The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$. The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_albd_jk_best.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_area_ik_best.pdf}
    \end{center}
    \end{minipage}
    \caption{Solution with smallest regularization term when $\Delta_t=1.75$ ($\Delta \phi = 90^{\circ }$).}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[b]
%    \begin{minipage}{0.5\hsize}
%    \begin{center}
%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
%    \end{center}
%    \end{minipage}
%    \begin{minipage}{0.5\hsize}
%    \begin{center}
%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
%    \end{center}
%    \end{minipage}
%    \caption{Solution with smallest regularization term. }
%\label{fig:regterm}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Fitting with $f$}

What if $f$ is used instead of $\fast$ in fitting?

From equation (\ref{eq:d_f_s}), the solution for $f_{lk} s_{kj}$ that is found through the least-square method is
%%%
\begin{equation}
\sum_i (W^{+})_{li} d_{ij} = \sum_k f_{lk} s_{kj}
\end{equation}
%%%
So, with an analogy to equation (\ref{eq:d_f_ast_s}), we could make similar plots of the principal components plane (with the principal components found from $\sum_i (W^{+})_{li} d_{ij}$ instead of $d_{ij}$).

Then, the regularization term would be $\mathcal{F}^{\ast } (\Delta_{\phi }; f) = \lambda ^2 \mathcal{F}$ will be used where
%%%
\begin{equation}
\mathcal{F}(\lambda, \Delta_{\phi }; f)\equiv  \sum _k \sum_{i,\,i'} (f^{T})_{ki} \Sigma_{ii'} ^{-1} f_{i'k}. 
\end{equation}
%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast }$ with $\Delta_t\sim 1.25$. The difference between the three panels is just the seed for \url{np.randam.uniform}.}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_albd_jk_best.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_area_ik_best.pdf}
    \end{center}
    \end{minipage}
    \caption{Solution with smallest regularization term when $\Delta \phi = 90^{\circ }$. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
